Continuations via Negative Information Flow

### 2012-02-14 dual.tex
added a couple of sentences in intro

>>>>

For a while we didn't know how to interpret the pair $(2,-3)$. I was thinking
that it corresponds to having two things: the value $2$ and the continuation
$3$. This makes no sense because $(2,-3)$ is isomorphic to $-(2,3)$. Instead
the right interpretation is that $(2,-3)$ corresponds to having 2
$3$-continuations which is the same as having a $6$-continuations or 3
$2$-continuations and so on.

Since Filinski, we've had the idea that values and continuations are like
mirror images. In a conventional language, the negative (continuation) side
is implicit and we introduce information effects on the positive. Trying to
recover the duality from this distorted positive side has always been
messy. Now it looks clean because we have kept the positive side pure.
